\plaintitle

### 2016-09-12 drafts/labor/complexity.tex
complexity should be kind of done

\subsubsection[finding crowdwork's limits]{Achieving greater complexity}\label{sec:complexity}
\ali{maybe a subssubsubsusbsubsection on the result/implication?
more people can make crowd tasks, but the algiorithmic manag}

\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants%
, interpreting medical data, and
telling coherent and compelling stories%
, to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

@@

\subsubsubsection{\pieceworkpers}
\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539}%
, who describes piecework as
    ``\dots~based on examination of various shop jobs,
      which included calculation of the standard time and compensation for each task''%
, argues that piecework must be rigorously evaluated at a time that demands
\textit{other people} perform the evaluation.
% \cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
This criterion strictly limits the extent to which piecework can grow in complexity;
it must, for instance, be quickly evaluable by another person.

@@

@@

\topic{Technology more directly facilitates the subversion of expertise requirements
by giving non--experts access to information that would otherwise be unavailable.}
Taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity.
Researchers have identified significant growth of
the hippocampal regions of the brains in veteran drivers%
, generally understood to be responsible for spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625%
,       skok2000managing,Woollett1407,woollett2011acquiring}.
Services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to know more about a city even than experts through
the collective data generated by other users
ranging topics such as police activity, congestion, construction, etc\dots
\cite{silva2013traffic,hind2014outsmarting}.

\topic{Crowdsourcing falters when the routinization of complex work proves difficult.}
\ali{Something about complexity being difficult to make routine when
there are lots of little, varied, unpredictable tasks (nod to \citeauthor{Brown01041990})}

>>>>

% \renewcommand{\topic}[1]{#1}
\subsubsection[finding crowdwork's limits]{Achieving greater complexity}\label{sec:complexity}
\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants%
, interpreting medical data, and
telling coherent and compelling stories%
, to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

@@

\subsubsubsection{\pieceworkpers}
\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539} describes a case study in Santa Fe Railway, which
deployed scientific management and a piecework regime in an attempt to stymie rising repair costs
\cite{10.2307/23702539}.
Returning to \citeauthor{hart2016rise}'s reflections on piecework's limitations,
we recall the multidimensional problem
--- tasks comprising of numerous, sometimes conflicting, goals
\cite{hart2016rise}.
It would be reasonable, then, to infer that work like this
--- reasonably highly skilled work where quality is difficult to assess ---
would be unsuitable for piecework.

\topic{\citeauthor{hart2016rise} and \citeauthor{10.2307/23702539}%
, without acknowledging one another%
, seemingly corroborate one another's conclusions at different levels of observation.}
\citeauthor{10.2307/23702539} enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and `experts'\dots''
\cite{hart2016rise,10.2307/23702539}.
\citeauthor{10.2307/23702539} and \citeauthor{hart2016rise} may seem
to be making differing claims about the limitations of piecework, but
we argue that \citeauthor{10.2307/23702539}
is simply making a more concrete observation illustrating the insight that
\citeauthor{hart2016rise} later makes.
\citeauthor{10.2307/23702539} recognizes that
it's necessary for a successful piecework shop to employ
clerks,
inspectors, and
other experts to properly design and evaluate complex work.
\citeauthor{hart2016rise} argues an ultimate limit to how far this can go;
at some point, evaluating multidimensional work output for quality
(rather than for quantity) becomes infeasible.

@@

\topic{There are other characteristics to effective complex piecework institutions, such as
appropriately designed management practices.}
\citeauthor{10.2307/2118435} describe the role of the foreman in West Virginia coal mines under the piecework model:
``The foreman had the power to hire and fire workers and allocate workplaces,
but then left the face--worker largely free to his own efforts so that
often he went all day without seeing the foreman''
\cite{10.2307/2118435}.
The general approach adopted by these West Virginia mines was,
as in other factories with active foremen,
to let the foreman be the intermediary between management and the worker.
Specifically, foremen were responsible for allocating resources and
understanding when and how to modify work as necessary
\cite{wray1949marginal}.

@@

\topic{Furthermore, technology more directly facilitates the subversion of expertise requirements
by giving non--experts access to information that would otherwise be unavailable.}
Taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity.
Researchers have identified significant growth of
the hippocampal regions of the brains in veteran drivers%
, generally understood to be responsible for spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625%
,       skok2000managing,Woollett1407,woollett2011acquiring}.
Services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to know more about a city even than experts through
the collective data generated by other users
ranging topics such as police activity, congestion, construction, etc\dots
\cite{silva2013traffic,hind2014outsmarting}.

\subsubsubsection{\implication}
\topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
it also signals some of the ultimate limitations of crowdwork and piecework in general.}
While the threshold preventing task requesters from utilizing piecework
has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly.
If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
we would benefit from finding ways to decompose varied tasks into homogeneous microtasks.

We should also consider exploring the limitations that algorithmic management bring along more carefully.
While research has touched on this subject, we've yet to make out the bigger picture of this theme
\cite{uberAlgorithm}.
If we can resolve the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest,
then we may be able to break a toxic cycle of mistrustful requesters \cite[for example][]{MaliciousCrowdworkersGadiraju}
and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
\cite{takingAHITMcInnis}.

% \topic{Crowdsourcing falters when the routinization of complex work becomes too difficult.}
% \ali{Something about complexity being difficult to make routine when
% there are lots of little, varied, unpredictable tasks (nod to \citeauthor{Brown01041990})}
